Single-step Hybrid Predition

### 2016-12-09 reports/single_step_kernels.Rmd
Add nested pred-names to untransformed kernels

# As a requirement of the kernel-generating functions, add the names of the 
# hybrid parents to each predictor-set/group combination.
cat_lst <- lapply(seq_along(feat_lst), FUN = function(i) {
  x_lvl1 <- feat_lst[[i]] 
  y_lvl1 <- hybrid_parent_nms[[i]]
  geno_lst <- lapply(seq_along(x_lvl1), FUN = function(j) {
    x_lvl2 <- x_lvl1[[j]]
    y_lvl2 <- y_lvl1[[j]]
    x_lvl2[["geno"]] <- y_lvl2
    x_lvl2
  })
  names(geno_lst) <- names(x_lvl1)
  geno_lst
})
names(cat_lst) <- names(feat_lst)

>>>>

# As a requirement of the kernel-generating functions, add the names of the 
# hybrid parents to each predictor-set/group combination.
cat_lst <- lapply(seq_along(feat_lst), FUN = function(i) {
  x_lvl1 <- feat_lst[[i]] 
  y_lvl1 <- hybrid_parent_nms[[i]]
  lvl1_nms <- x_lvl1 %>%
    names() %>%
    str_replace_all(., pattern = "_none", replacement = "") %>%
    strsplit(., split = "_")
  geno_lst <- lapply(seq_along(x_lvl1), FUN = function(j) {
    x_lvl2 <- x_lvl1[[j]]
    y_lvl2 <- y_lvl1[[j]]
    names(x_lvl2) <- lvl1_nms[[j]]
    x_lvl2[["geno"]] <- y_lvl2
    x_lvl2
  })
  names(geno_lst) <- names(x_lvl1)
  geno_lst
})
names(cat_lst) <- names(feat_lst)
